Discovering governing reactions from concentration data

### 2018-01-23 docs/manuscript.tex
manuscript update

@@

	%\begin{figure}
	%	\begin{center}
	%		\includegraphics[width=.5\textwidth]{./figures_tex/aux_linear_approximation.eps}
	%	\end{center}
	%	\caption{This figure depicts a possible output yielded by an application of the Gillespie method and the performed piecewise linear approximation in order to obtain a better behaving derivative.}
	%	\label{examples:linear-approximation}
	%\end{figure}

	(\textcolor{red}{this has changed, rewrite!})

	For generating time series data of concentrations we use the Gillespie method \cite{Gillespie1976}. For given initial conditions, we produce several realizations which then are converted to a trajectory with fixed time step and averaged. Since these trajectories are piecewise constant, one has to take special care when approximating the data's temporal derivative that is needed in (\ref{method:minimizationproblem}). Applying finite differences has the effect that, with decreasing time step, the derivative mostly constant zero and approaches infinity at the jump discontinuities. To counter this effect, we beforehand perform a linear approximation between each two adjacent discontinuities, as depicted in Figure \ref{examples:linear-approximation} and thus obtain a piecewise constant derivative. (\textcolor{red}{Use regularized derivative?})

>>>>

	When presented with multiple trajectories one can extend the objective function by a sum over these and obtain a more general minimization problem that reads: Find $\hat{\Xi}$ such that
	\begin{align}
		\hat{\Xi} = \underset{\Xi}{\arg\min}\left( \sum_{\text{traj}}\frac{1}{2T_{\text{traj}}}\left\| \dot{\textbf{X}_\text{traj}} - \Theta(\textbf{X}_\text{traj})\Xi \right\|_F^2 + \alpha\lambda\|\Xi\|_1 + \alpha(1-\lambda)\|\Xi\|_2^2 \right)
	\end{align}
	subject to $\Xi\geq 0$. (\textcolor{red}{this probably should be motivated better})

@@

	For generating time series data of concentrations we integrate the law of mass action equations and add Gaussian noise. In that manner we produce several realizations for a couple of initial conditions. The derivatives are evaluated by finite differences of first order.
